### 2022-02-22 README.Rmd

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

@@

# Jittered trip data

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
library(sf)
```

@@

```{r}
od_all = readRDS("TRIPSmode_freguesias.Rds")
zones = readRDS("FREGUESIASgeo.Rds")
od_all_sf = od::od_to_sf(od_all, zones)
od_all_jittered = readRDS("od_all_jittered_50.Rds")
```

The OD datasets, before and after jittering, are shown below.

```{r jitteredoverview, out.width="50%", fig.show='hold'}
plot(od_all_sf$geometry, lwd = 0.2)
plot(od_all_jittered$geometry, lwd = 0.1)
```
